---
title: Using impress.js with Quarto
subtitle: Make those slides swirl
date: last-modified
author: Till Krenz
abstract: The other day over on [stackoverflow](https://stackoverflow.com/q/77146042/4821142) [user113156](https://stackoverflow.com/users/6447399/) asked if there is a way to create [Impress.js](https://github.com/impress/impress.js) presentations with Quarto. I created a [minimal example](https://stackoverflow.com/a/77146457/4821142) of a `qmd` file that renders into a impress.js presentation. To make the process more easy, I created a Quarto extension. So now you can get started with your prezi-style presentations with Quarto by simply installing the impress.js extension.  
format: 
  impressjs-html
execute: 
  echo: false
---

::: {#overview-start .step data-scale=3}

:::


::: {#textseq1a .step data-x="1500"}

You can have **sequences of text blocks**.

:::

::: {#textseq1b .step data-x="2200" data-rotate="90" .big}

That rotate.

:::

::: {#textseq1c .step data-x="1500" data-y="700" data-rotate="540" }

[And swirl around.]{.big}

:::

::: {#textseq1d .step data-x="1500" data-y="-700" data-rotate-x="45"  data-max-scale="3" data-min-scale="0"}

[So.]{.big}
[Cool.]{.big .substep}
[😎]{.big .substep}

:::


::: {#slide1a .step .slide data-x="0" data-y="-1000"  data-rotate-z="0"}

You can have r output on slides.

```{r}
#| fig.height: 6
#| message: false
library(tidyverse)
library(ggplot2)

mtcars |> 
  as_tibble(rownames = "car") |> 
  ggplot() +
  geom_col(aes(reorder(car, disp), disp, fill = disp)) +
  scale_fill_continuous(type = "viridis") +
  coord_flip() +
  theme_minimal() +
  labs(y = "displacement")
```

:::

::: {#slidebehindslide1a .step .slide data-y="-1000" data-scale=".1" data-z="-1000"}

And slides with more R output - **behind** your slides.

```{r}
mtcars |> 
  as_tibble(rownames = "car") |> 
  mutate(angle = (qsec - min(qsec)) / (max(qsec) - min(qsec)) * 180 - 90) |> 
  ggplot(aes(disp, qsec, label = car)) +
  geom_point(aes(color = -qsec)) +
  scale_color_continuous(type = "viridis") +
  coord_flip() +
  geom_text(aes(angle = angle), size = 2, hjust = -.1) +
  theme_minimal() +
  labs(x = "displacement", y = "time to travel 1/4 mile")
```

:::


::: {#wait .step .slide data-x="-15500" data-y="-1000" data-scale="10"}

[But wait!]{.big}
This just in...

:::


::: {#breaking .step .slide data-x="-15500" data-y="-1050" data-rotate="5000" data-scale="0.1" data-z="1000"}

[BREAKING NEWS!]{.medium}

Building [Quarto Extensions](https://quarto.org/docs/extensions/) is fun! You should [build your own](https://quarto.org/docs/extensions/creating.html), explore other extensions and [check out](https://github.com/mcanouil/awesome-quarto#contents) presentations, articles, and more created with Quarto and its extensions.
<br><br>
Now back to Quarto and impress.js.

:::

::: {#noslideR .step data-y="-1000" data-x="-1500" data-rotate-x="360"}

R output can also be in a non-slide step.

```{r}
#| classes: .substep
library(gt)

mtcars |> 
  summarise(across(disp:qsec, mean), .by = cyl) |> 
  gt() |> 
  fmt_number(decimals = 1)
```
:::


::: {#manual1 .step data-y="0" data-x="-1500"}

## How To add and animate steps?

<br>

Use div fences `:::` in your quarto file and add the `.step` class.

[Add the `.substep` class to an element to successively show substeps.]{.substep}

[Use `data-x`, `data-y`, `data-z` `data-rotate`, `data-scale`, ... to position and arrange steps.]{.substep}

:::


::: {#manual2 .step data-y="1000" data-x="-1500"}

## Install & Configure

- `quarto install ...`

- add your content

- edit css

:::

::: {#end .step data-y="1000" data-x="0"}

That's it!

[The End.]{.big .substep}

:::


::: {#overview-end .step data-scale=3 data-x="0" data-y="0"}

:::